\section{Evaluation}
\label{sec:evaluation}

%------------------------------------------------

The \ac{acm} maintains an annual writeup of guidelines for undergraduate computer science education.~\cite{CS2013}
These guidelines include two important sections, the Exemplar Courses and Knowledge Areas.
The Knowledge Areas are 18 broad topics within Computer Science as put forth by the \ac{acm}.
Exemplar Courses include real course descriptions from disparate sources compiled by the \ac{acm} and manually annotated with the Knowledge Areas they cover.
These data sets are used to perform primary evaluation.

%------------------------------------------------

Using manually annotated course descriptions (the \ac{acm} Exemplar Courses or the George Mason University Computer Science department courses\footnote{\url{http://cs.gmu.edu/~white/Curriculum2013}}) as a ground truth label set, Knowledge Area predictions are compared against known Knowledge Areas.
Knowledge Areas predictions are made by determining which Knowledge Areas share inferred topics with each course in a department.
Evaluation is performed by computing the similarity between the predicted and ground truth Knowledge Area labels.
The label set similarity is computed in two ways.
First, the Jaccard index of the predicted and ground truth labels is calculated.
Then, the percent of the ground truth labels included in the prediction set is calculated.
The results of evaluating George Mason University's Computer Science department in this way across the 77 Result Sets are summarized in \tref{tbl:evaluation-before}.
However, after removing result sets where less than one knowledge area was predicted on average per course, results were improved.
These improved results are summarized in \tref{tbl:evaluation-after}.

%------------------------------------------------

\begin{table}[ht]
\centering
\begin{tabular}{lll}
\toprule
& Jaccard & Percent \\
\midrule
mean   & 0.145 & 0.229 \\
median & 0.156 & 0.217 \\
\midrule
max    & 0.007 & 0.007 \\
min    & 0.311 & 0.709 \\
\bottomrule
\end{tabular}
\caption{Evaluation of all result sets\label{tbl:evaluation-before}}
\end{table}

%------------------------------------------------

\begin{table}[ht]
\centering
\begin{tabular}{lll}
\toprule
& Jaccard & Percent \\
\midrule
mean   & 0.203 & 0.377\\
median & 0.206 & 0.351\\
\midrule
max    & 0.058 & 0.082\\
min    & 0.311 & 0.709\\
\bottomrule
\end{tabular}
\caption{Evaluation of result sets with more than one predicted knowledge area on average per course\label{tbl:evaluation-after}}
\end{table}

%------------------------------------------------

