\documentclass{beamer}

\usepackage{booktabs}
\usepackage{color}
\usepackage{graphicx}
\usepackage[backend=bibtex]{biblatex}

\title[Curricula and LDA]{Unsupervised academic curricula evaluation
  through Latent Dirichlet allocation}
\author{Jean Michel Rouly \and Huzefa Rangwala}
\date{Updated \today}

\usetheme{Boadilla}
\usecolortheme{rose}

\bibliography{../bibliography/bibliography.bib}

\begin{document}

  \frame{\titlepage}

  \include{slides/research-goal}

  \include{slides/background-domain}

  \include{slides/background-ml}

  \include{slides/lda}

  \begin{frame}{Timeline}
    \begin{itemize}
      \item {\color<2>{green}Complete CS 390.}
      \item {\color<2>{green}Continue building university dataset.}
      \item {\color<2>{green}Improve text cleaning technique.}
      \item {\color<2>{green}Test out topic modeling on new dataset.}
      \item Test out topic modeling on prerequisite chains and model
        concept overlap.
      \item {\color<2>{green}Architect and install database layer between
        Scrape and Learn.}
      \item {\color<2>{red}Write database hooks for visualization
        software.}
      \item Build visualization tool that hooks into database.
    \end{itemize}
  \end{frame}

  \include{slides/resources}

  \include{slides/framework}

  \begin{frame}{Proposed visualization tool}

    \only<1>{
      \begin{itemize}
        \item Import results of the LDA function back into the database
          layer, possibly with pedigree data (ie.\ knowledge of which run
          what data came from) Link it all up back to the existing scraped
          meta information.
        \item Host the database as a backend to a simple responsive
          user-facing browser-based web application.
        \item Feature: visualization of data, possibly graph-based.
        \item Feature: query interface allowing user to search through
          mined and inferred data sources.
      \end{itemize}
    }

  \end{frame}

  \include{slides/goals}

\end{document}
