\documentclass{beamer}

\usepackage{booktabs}
\usepackage{color}
\usepackage{graphicx}
\usepackage[backend=bibtex]{biblatex}

\title[Curricula and LDA]{Unsupervised academic curricula evaluation
  through Latent Dirichlet allocation}
\author{Jean Michel Rouly \and Huzefa Rangwala}
\date{Updated \today}

\usetheme{Boadilla}
\usecolortheme{rose}

\bibliography{../bibliography/bibliography.bib}

\begin{document}

  \frame{\titlepage}

  \include{slides/research-goal}

  \include{slides/motivation}

  \include{slides/background-ml}

%  \include{slides/lda}

  \begin{frame}{Progress so far}
    \begin{itemize}
      \item Collect preliminary course description dataset.
      \item Perform exploratory clustering.
      \item Expand initial prototype to include LDA computation.
      \item Build preliminary visualization tool.
      \item Run LDA experiments varying initialization parameters.
      \item Construct course prerequisite trees.
      \item Implement metrics for department/course comparison.
    \end{itemize}
  \end{frame}

  \include{slides/framework}

  \include{slides/resources}

%  \include{slides/preliminary-results}

  \begin{frame}{Visualization tool}

    \begin{itemize}
      \item Interactive browser-based application.
      \item Allows both high level overview of dataset and low level view of per-course topic inferences.
      \item Provides view of
        \begin{itemize}
          \item topics
          \item departmental comparison
          \item prerequisite chains
          \item dataset dashboard
        \end{itemize}
    \end{itemize}
  \end{frame}

%  \begin{frame}{Proposed visualization tool}
%
%    \only<1>{
%      \begin{itemize}
%        \item Import results of the LDA function back into the database
%          layer, possibly with pedigree data (ie.\ knowledge of which run
%          what data came from) Link it all up back to the existing scraped
%          meta information.
%        \item Host the database as a backend to a simple responsive
%          user-facing browser-based web application.
%        \item Feature: visualization of data, possibly graph-based.
%        \item Feature: query interface allowing user to search through
%          mined and inferred data sources.
%      \end{itemize}
%    }
%
%  \end{frame}

%  \include{slides/goals}

%  \begin{frame}
%  \begin{center}
%  \Huge Questions?
%  \end{center}
%  \end{frame}

\end{document}
